Proposed Solution

### 2016-01-29 intro1.tex
lala
random

\section{Introduction}

@@

Such solutions typically incur high administration cost (\eg, 
requiring users to write pattern-matching scripts) 
and are unreliable (\eg, some errors may show no user-visible symptoms).
These shortcomings often lead to prolonged delays between
the occurrence and the detection of errors, thus causing unrecoverable
damage to system states.

We expect to explore a fundamentally different means to tackle 
the misconfiguration problem. Rather than using retroactive approaches
to deal with configuration errors after the software failures occur, 
we would like to {\em proactively} prevent misconfiguration problems 
{\em before} users first deploy the configuration files to 
their system settings. In other words, we aim to offer users 
a configuration error filter in order to significantly minimize 
the probability of misconfigurations in the system runtime.

Based on the above intuition, this paper presents \app, 
a proactive misconfiguration checker which takes users' 
configuration files as input and then reports potential configuration 
errors to the users before they deploy their systems 
according to these configurations.
At the heart of \app lies a machine learning mechanism, 
which learns rules and constraints from pluggable 
correct sampling configuration files (\ie, for the training purposes), 
and then detects errors violating the learned constraints.

\app mainly offers users three significant benefits.
First, there is no any extra burden added to users who only need to 
simply use \app as a ``seamless'' pre-checker for their configurations.
Second, because many misconfiguration errors have been eliminated 
by \app, the workloads of post-failure forensics in runtime
are significantly reduced, thus making these tools truly practical.
Finally, since there have been many correct but not specific 
example configuration files in practice, 
increasingly more samples can be freely added to \app,
thus giving \app evolutionary capability.

Using these ideas, we make the following contriubtions:

@@

  \item Our tool, \app can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
  \item We present a probabalistic type that can be used to assign a confidence distribution over a set of types to a valule.
  \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

>>>>

\section{Introduction and System Overview}
\label{sec:Intro}

@@

We propose an approach to the verification of  
configuration files which is based on learning rules about the language 
model for configuration files.

\begin{figure}[t] \centering
\includegraphics[width=0.8\textwidth]{figs/overview}
\caption{An overview of the \app's workflow.}
\label{fig-overview}
\end{figure}

Fig.~\ref{fig-overview} describes an overview of our system. We start with
an assumption that we are given a number of correct configuration files belonging to the same category (for instance, MySQL or Apache). Such files
follow the same naming conventions and we use that fact in a learning 
algorithm which will result with the rules describing the language model used in the files. Since the ``language'' of configuration types is untyped and unstructured, we first parse the files and translate them 
into a more structured, typed, intermediary representation. Having more structured files, we use them as a training set to learn the rules about the 
language model. These rules are used for detecting errors violating the learned constraints in the files given by the user.

From a  practical perspective there is no additional burden 
to the users: they can use \app to verify their configuration files.

Second, because many misconfiguration errors have been eliminated 
by \app, the workloads of post-failure forensics in runtime
are significantly reduced, thus making these tools truly practical.
Finally, since there have been many correct but not specific 
example configuration files in practice, 
increasingly more samples can be freely added to \app,
thus giving \app evolutionary capability.

Using these ideas, we make the following contributions:

@@

  \item Our tool, \app can learn a language model from a set of examples of correct configuration files, and use the model to verify new files.
  \item We present a probabilistic type that can be used to assign a confidence distribution over a set of types to a value.
  \item In \app, we define a minimal interface for describing a verification attribute in a learning context, making it easy to add new rules to the system.

### 2016-01-29 system.tex
random

\section{\app Design}

\begin{figure}[t] \centering
\includegraphics[width=0.8\textwidth]{figs/overview}
\caption{\app's workflow overview.}
\label{fig-overview}
\end{figure}

\xxx{
\app Design: 
  \begin{itemize}
  \item Present an architecture of \app with a fig. Briefly describe 
    how it works (step by step).
  \item Detail learner part
  \item Merge
  \item Check 
  \item Limitations
  \end{itemize}
}

>>>>

\section{Quantum Types}

Because our type inference is based on machine learning, we cannot be sure that a keyword unambigously has a single type.
This is an issue when we try to learn relational rules between keywords. 
Take the following file in the learning

foo = 300
bar = 300.txt

We want to learn the rule that $foo \in {substring(bar)}$, however using unambigous type inference, we would assign foo type int, and never try to generate a string relation rule for these two keywords.
By assigning foo a quantum type (e.g. ${Int <90\%>, String <10\%>}$), we can now generate rules for both types.

At runtime, when the user wants to check a file we update the probabilities one last time then 'collapse' the quantum type to a concrete type.
If the concrete type collapses to a Int, we consider the rules for ints, and vice versa.

This idea is closely related to exstentially quantified types.
